State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
some edition to the smoother
fixed the reference to the Appendix E

where the superscripts $m$ and $c$ stand for mean and covariance. Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are  used to correct the predicted states. The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above. To compute the smoother gain, the predicted cross-covariance matrix of the states is used with the covariance matrix. A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}. It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive. Therefore, the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms. The additive disturbance form reduces the dimension and the number of sigma points used in the algorithm.

@@

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{LeastSquaresAppendix}).

>>>>

where the superscripts $m$ and $c$ stand for mean and covariance. Since the observation equation is linear (equation~\ref{ObservationEquation}) the standard Kalman Filter update equations are  used to correct the predicted states. The state estimates from the forward filtering are used to form a new set of sigma points for the smoother, as described above. To compute the smoother gain, the cross-covariance matrix of the states, $\mathbf M$, needs to be computed. A summary of the URTSS procedure is given in Algorithm~\ref{UKFAlgorithm}. It should be noted that  the disturbance, $e_t\left(\mathbf{r}\right)$ and the measurement noise, $\boldsymbol{\varepsilon}_t$, are additive. Therefore, the additive form of the URTS is used, otherwise the state vector should be augmented with the noise terms. The additive disturbance form reduces the dimension and the number of sigma points used in the algorithm.

@@

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a least squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new state vector sequence estimate (see~\ref{App:LeastSquaresAppendix}).
